Reanalysis Step 1: Data Preparation

### 2025-08-14 reanalysis-1-data_preparation.qmd
wip

1. **Glaucoma/Other Retina Conditions**: Missing values are recoded as 0 (absence of condition)
   - Clinical assumption: These conditions would be documented if present
   - This recoding happens BEFORE propensity score modeling
   - Maintains consistency with original analysis

2. **CCI/DCSI**: **NEW - Will be imputed** (change from original analysis)
   - Original analysis excluded rows with missing CCI/DCSI
   - Reanalysis will impute these to preserve sample size and reduce bias
   - These comorbidity indices can be reliably imputed from patient demographics and clinical characteristics

>>>>

1. **Glaucoma/Other Retina Conditions**: Missing values are recoded as 0 (absence of condition)
   - Clinical assumption: These conditions would be documented if present
   - This recoding happens BEFORE propensity score modeling
   - Maintains consistency with original analysis
   - **Is this assumption valid?** Do we want to impute these?

2. **CCI/DCSI**: **NEW - Will be imputed** (change from original analysis)
   - Original analysis excluded rows with missing CCI/DCSI
   - Reanalysis will impute these to preserve sample size and reduce bias
   - These comorbidity indices can be imputed from patient demographics and clinical characteristics
